\thetitle

### 2021-06-27 writing/results.tex
results: Fix wrapfigure (10)
Fix wrapfigure placement
Fix grammar and typos
Fix old leftover discussion in results section

\
\begin{figure} \footnotesize 
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}

@@

The figure answers questions $Q_1$, $Q_2$ and $Q_3$ affirmatively.  
In all three semantics, blame modes outperform their
corresponding exception mode by \textasciitilde10\%.  The
Natural exceptions mode is never more useful than Natural blame, and
Transient exceptions are more useful than Transient first and Transient
last blame in a small percentage (less than 1\%) of the scenarios.

@@

Second, the exceptions of the Erasure semantics either help the rational
programmer immediately or the rational programmer fails to debug a scenario
altogether (in red).  This is expected; adding type annotations to an Erasure
program does not change its behavior, so if the type checker does not reject the
program with the new annotations, the rational programmer is stuck.  In other
words, an exception from the run-time system has to point to the buggy module with the
first try. Otherwise the rational programmer types an irrelevant module, runs
the program again, and the same exception points again to the already typed
module.

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of effort.
The comparison between two modes boils down to the difference in length between
their trails for all scenarios where they both succeed. Hence, each plot in the
figure shows the distribution of scenarios with length differences ranging from
-3 (the first mode's trail is 3 steps shorter than the second's) to 3 (the first
mode's trail is 3 steps longer than the second's). The figure offers several
insights about how modes compare in terms of effort that complement the insights
about how they compare in terms of success rates from figure~\ref{fig:avo-bars}.
First, Natural blame never produces shorter trails than Natural exceptions, and
sometimes (albeit rarely) produces slightly longer ones. Hence, the experiment
provides evidence that blame helps the rational programmer debug more scenarios
but does not shorten the debugging process compared to exceptions. Second,
Natural relatively often (close to 8\% of the scenarios) produces shorter trails
than both Transient blame modes, and sometimes the trails are significantly
shorter. Finally, Transient's blame modes also share the characteristic with
Natural that blame sometimes produces longer trails than their corresponding
exception modes.

>>>>

\begin{figure} \footnotesize 
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}

@@

The figure answers questions $Q_1$, $Q_2$, and $Q_3$ affirmatively.
In all three semantics, blame modes outperform their
corresponding exception mode by \textasciitilde10\%.  The
Natural exceptions mode is never more useful than Natural blame, and
Transient exceptions are more useful than Transient first and Transient
last blame in a small percentage (less than 1\%) of the scenarios.

@@

Figure~\ref{fig:effort-comparisons} provides head-to-head comparisons of effort.
The comparison between two modes boils down to the difference in length between
their trails for all scenarios where they both succeed. Hence, each plot in the
figure shows the distribution of scenarios with length differences ranging from
-3 (the first mode's trail is 3 steps shorter than the second's) to 3 (the first
mode's trail is 3 steps longer than the second's). The figure offers several
insights about how modes compare in terms of effort that complement the insights
about how they compare in terms of success rates from figure~\ref{fig:avo-bars}.
First, Natural blame rarely produces shorter trails than Natural exceptions, and
occasionally produces slightly longer ones. Hence, the experiment
provides evidence that blame helps the rational programmer debug more scenarios
but does not shorten the debugging process compared to exceptions. Second,
Natural relatively often (close to 8\% of the scenarios) produces shorter trails
than both Transient blame modes, and sometimes the trails are significantly
shorter. Finally, Transient's blame modes share the characteristic with
Natural that blame sometimes produces longer trails than their corresponding
exception modes.
